Title of the document here

### 2015-02-06 rmtw/assignment_1/assignment_1.tex
Results analysis

\SubSection{Results Analysis}
TODO:
* Describe  and motive  method  for analyzing the data

Results Anal
- Present data 
- Check for response bias
- conduct descriptive analysis
- collapse items into scales
- check for reliability of scales
- Run inferential statistics to answer research question or results
** If number is too small, do we stop there?
- How will the results be interpreted?

@@

\begin{tabular}{| l | r | c |}
	\hline
	\textbf{Variable Name} & \textbf{Research Question} & \textbf{Item on Survey} \\ \hline
	Occupation & RQ1, SQ1 & \\ \hline
	Experience & RQ1, SQ1 & \\ \hline
	Preferred Language & RQ1, SQ2 & \\ \hline
	Least Preferred Language & RQ1, SQ2& \\  \hline
	Working Language & RQ1, SQ2 & \\ 
	\hline
	\end{tabular}

>>>>

\SubSection{Results Analysis}
The response rate for the questionnaire was 11\%. The questionnaire was distributed to 270 members of the sample group and 29 members returned the survey. An additional 6 students have answered the questionnaire in a second iteration, where they were personally contacted based on which year they were attending. Table XXX1 displays information of the respondents experience level. Table XXX2 shows the year which the students are attending. 
\newline

\begin{table}[ht]
  \centering
  \begin{tabular}{| l | r |}
    \hline
    \textbf{Experience} & \textbf{Distribution} \\ \hline
    Less than a year & 70\% \\ \hline
    Between 1 and 3 years & 20\% \\ \hline
    More than 3 years & 10\% \\ 
    \hline
  \end{tabular}
  \caption{ Hiadsdsafdsaf}
\end{table}

\begin{table}[ht]
  \centering
  \begin{tabular}{| l | r |}
    \hline
    \textbf{Academic Year} & \textbf{Distribution} \\ \hline
    1st year & 80\% \\ \hline
    2nd year & 15\% \\ \hline
    3rd year & 5\% \\ 
    \hline
  \end{tabular}
  \caption{ Hiadsdsafdsaf}
\end{table}

Response bias has been determined mostly through analysing the correlation between the independent variables and the dependent variables. Readability of a language is likely to be strongly correlated with the reader's experience of the language. Due to there being a high response rate amongst 1st year students, it suggests that the nonrespones may have affected the results. This is not necessarily negative, since our study aims to measure the inherent readability of a programming language, where the experience of the reader has as little effect as possible. 
\newline

The data was collected with a questionnaire consisting of 15 questions.
Re

Results Anal

- conduct descriptive analysis
- collapse items into scales
- check for reliability of scales
- Run inferential statistics to answer research question or results
** If number is too small, do we stop there?
- How will the results be interpreted?

@@

\begin{table}[ht]
  \centering
  \begin{tabular}{| l | r | c |}
  	\hline
  	\textbf{Variable Name} & \textbf{Research Question} & \textbf{Item on Survey} \\ \hline
  	Experience & RQ1, SQ1 & 1 \\ \hline
    Academic Year & RQ1, SQ1 & 2 \\ \hline
  	Preferred Language & RQ1, SQ2 & 3 \\ \hline
  	Least Preferred Language & RQ1, SQ2& 4 \\  \hline
  	Experience of Language & RQ1, SQ2 & 5 \\ 
  	\hline
	\end{tabular}
  \caption{ Hiadsdsafdsaf}
\end{table}
